---
title: "Documentation for `get_bw_score` Function"
author: "Md Aminul Islam Prodhan"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

The `get_bw_score` function is designed to compute the binding-weighted (BW) score for a given set of target predictions. It takes in a data frame of predictions and a binding threshold to calculate a score that reflects the relevance of binding targets.

## Function Signature

```{r}
get_bw_score <- function(df, binding_threshold) {
  # Function implementation
}
```

# Arguments

- `df`: A `data.frame` containing at least two columns:
  - `prob`: Numeric values representing predicted binding probabilities.
  - `affinity`: Numeric values representing binding affinity.

- `binding_threshold`: A numeric value indicating the minimum probability required to consider a prediction as binding.

# Return Value

A numeric value representing the binding-weighted score, calculated as the weighted sum of the affinities of the predictions that exceed the `binding_threshold`. The formula is:

\[
BW\_Score = \sum_{i \in \text{Binding}} P_i \cdot A_i
\]

where \(P_i\) is the binding probability and \(A_i\) is the binding affinity.

# Example Usage

```{r example}
# Example data frame
predictions <- data.frame(
  prob = c(0.8, 0.6, 0.4, 0.9),
  affinity = c(5, 3, 2, 7)
)

# Define binding threshold
threshold <- 0.5

# Compute the binding-weighted score
bw_score <- get_bw_score(predictions, threshold)
print(bw_score)
```

# Edge Cases

1. If the data frame `df` is empty, the function should return `0`.
2. If none of the `prob` values exceed the `binding_threshold`, the function should return `0`.
3. Ensure that both `prob` and `affinity` columns are numeric, and handle any invalid data types gracefully.

# Implementation Details

The function filters rows where the `prob` column exceeds the `binding_threshold` and computes the score using vectorized operations. This ensures efficiency and scalability for larger datasets.

# Additional Notes

- The function assumes the input data frame is correctly formatted. Pre-processing steps (e.g., missing value handling) should be performed beforehand.
- Users can customize the `binding_threshold` to match the specificity requirements of their analysis.
